### 2019-09-22 papers/journal/problem.tex
Updated the Spec text

%In the implementation, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%In the implementation, to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%
In the implementation instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system.

@@

%%\ankit{This is a dummy template. need a rewrite.} 
%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.

>>>>

%In the implementation, to conclude that a given $k$-connectedness is not a universal condition it is suffice to search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%In the implementation, to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment of all the rules of the system, i.e., checking the negation of the condition is unsatisfiable.
%

@@

For the efficient implementation of the specification instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
%
That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
%
In case no such graph exists for a specific $k$ we reported the corresponding $k$.
%%\ankit{This is a dummy template. need a rewrite.} 
%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
